{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2018-01-22 wacv-camera-ready.tex
Fixed Burak's suggestions.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. For such applications, it is
desirable for the deployed algorithms to run in high-speed and require
no offline training. To develop a single-target tracking algorithm
with these properties, we propose an ensemble of the kernelized
correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
is designed to specifically address the variations in scale and
translation of moving objects. To guarantee a high-speed run-time
performance, we deploy each of KCFs in turn, instead of applying
multiple KCFs to each frame altogether. To reduce any potential drifts
between individual KCFs' transition, we developed a particle
filter. Experimental results showed that the performance of ours is,
on average, 70.10\% for precision at 20 pixels, 53.00\% for success
rate for the OTB100 data, and 54.50\% and 40.2\% for the UAV123
data. Experimental results showed that our method is, on average,
better than other high-speed trackers over 5\% on precision on 20
pixels and 10-20\% on AUC. \textit{YoungWoo : Two preceeding sentences start with
experimental results showed that. Should we change the begining of the second sentence?}
In addition, our implementation ran at 340
fps for the OTB100 and at 416 fps for the UAV123 dataset that is
faster than DCF (333 fps) for the OTB100 and KCF (296 fps) for the
UAV123. To increase flexibility of the proposed {\it E}nKCF running on
various platforms, we also explored different levels of deep
convolutional features.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing mobile platforms. Among those technologies, computer vision
algorithms are getting more attentions primarily because payloads of
those mobile platforms are limited to carry any other sensors than a
monocular camera. Instead of just manually being flew for video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following function would make it more useful for the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on various events, many
others. \textit{YoungWoo : For me, it was hard to get the previous sentence.}
To this end, in this paper, we propose a single-target
tracking algorithm that does not require offline training and can run
at high-speed. Specifically, we would like to have our algorithm 1)
learn the appearance model of a target on the fly and 2) run on a
typical desktop as fast as $300$-$450$ fps.

@@

\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
conventional hand-crafted features, fHoG (shape)
\cite{felzenszwalb2010object} and color-naming (color)
\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
features. This setup of the {\it E}nKCF is designed to develop an
online tracking algorithm running at high-speed ($\ge$ 300 fps) on a
typical desktop (and eventually running $\ge 30$ fps on a low-end
embedded system without GPUs).
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small area translation filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large area translation filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features. The
  \textit{YoungWoo : the responses are target (desired) response for the correlations filters}
  responses by the large and small area translation filters and scale
  filter are represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$ and
  $y_{R_{s}}$.}
\label{fig:Filters}
\end{figure}

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm
with those of the state-of-the-art tracking algorithms. For the
precision, we rank the trackers based on the precision numbers at 20
pixels whereas in the success rate plots, they are ranked by the area
under curve (AUC) scores. The tracking algorithms under the comparison
include ones at high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones at relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers \textit{YoungWoo : it should be "use" I think.}originally uses deep
convolutional features, however, to perform fair comparison, we use
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
    at 20 pixels precision. In particular, three algorithms, SAMF,
    DSST, and Struck did about $5\%$ better than ours in accuracy, but
    10-20 times slower. The more recent trackers, ECO and CCOT, on the
    other hand, outperforms {\it E}nKCF by $15\%$ while running at
    10-15 times slower. For the scale adaptation, {\it E}nKCF did
    fourth best in terms of AUC for the success rate plot. It
    outperformed other high-speed trackers by about $20\%$-$25\%$ in
    AUC. In addition, it performed even better than some of the
    lower-speed trackers.  For example, for AUC, {\it E}nKCF
    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
    more than $10$ and $30$ times faster. For the DSST, we believe our
    algorithm outperformed it because, first of all, the DSST uses a
    1-D scale filter and searches the target's scale over 33
    candidates in a scale pool whereas our algorithm uses a 2-D scale
    filter with 3 candidate scales. Learning a 2-D filter resulted in
    learning more spatial information. Second of all, the DSST uses
    only fHoG whereas our algorithm uses both fHoG and color-naming
    features. Learning complementary features such as color and shape
    provided a better understanding of the ROI.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to performance comparison with other trackers, we
also conducted an experiment to see what combination and deployment
order of the KCF works best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. To achieve fair comparison, we
did not use the particle filter. The combination presented at the
$2^{nd}$ column switched the order of deploying $R_{t}^{L}$ and
$R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The combinations with the ``*'' marker ran the
filters on every frame in the listed order. The trackers at the
$7^{th}$ and $8^{th}$ columns ran a translation and a scale filter on
every frame which is similar to the LCT tracker
\cite{ma2015long}.\footnote{To be precise, the LCT tracker comes with
  a re-detection module for a long-term tracking.} This experiment
empirically verified that the way \textit{E}nKCF uses multiple KCFs is
optimal, in terms of both tracking accuracy and run-time
performance. For example, one could achieve $4.26\%$ higher in
accuracy by running $R_{t}^{L}$ and $R_{t}^{S}$, and $R_{s}$ at every
frame (produced 58.16\% for precision at 20 pixels), but this
combination decreases run-time performance to 317 fps (=416fps - 99fps). 
\textit{YoungWoo : Should it not be 99fps.}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications running on embedded systems. For such applications, it is
desirable for the deployed algorithms to run in high-speed and require
no offline training. To develop a single-target tracking algorithm
with these properties, we propose an ensemble of the kernelized
correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
is designed to specifically address the variations in scale and
translation of moving objects. To guarantee a high-speed run-time
performance, we deploy each of KCFs in turn, instead of applying
multiple KCFs to each frame altogether. To reduce any potential drifts
between individual KCFs' transition, we developed a particle
filter. Experimental results showed that 1) the performance of ours
is, on average, 70.10\% for precision at 20 pixels, 53.00\% for
success rate for the OTB100 data, and 54.50\% and 40.2\% for the
UAV123 data, and 2) our method is, on average, better than other
high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
AUC. In addition, our implementation ran at 340 fps for the OTB100 and
at 416 fps for the UAV123 dataset that is faster than DCF (333 fps)
for the OTB100 and KCF (296 fps) for the UAV123. To increase
flexibility of the proposed {\it E}nKCF running on various platforms,
we also explored different levels of deep convolutional features.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing mobile platforms. Among those technologies, computer vision
algorithms are getting more attentions primarily because payloads of
those mobile platforms are limited to carry any other sensors than a
monocular camera. Instead of just manually being flew for video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following function would make it more useful for the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on various events, many
others. To this end, in this paper, we propose a single-target
tracking algorithm that does not require offline training and can run
at high-speed. Specifically, we would like to have our algorithm 1)
learn the appearance model of a target on the fly and 2) run on a
typical desktop as fast as $300$-$450$ fps.

@@

\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
conventional hand-crafted features, fHoG (shape)
\cite{felzenszwalb2010object} and color-naming (color)
\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
features. This setup of the {\it E}nKCF is designed to develop an
online tracking algorithm running at high-speed ($\ge$ 300 fps) on a
typical desktop (and eventually running $\ge 30$ fps on a low-end
embedded system without GPUs).
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small area translation filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large area translation filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features. The
  responses by the large and small area translation filters, and scale
  filter represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$ and
  $y_{R_{s}}$.}
\label{fig:Filters}
\end{figure}

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm
with those of the state-of-the-art tracking algorithms. For the
precision, we rank the trackers based on the precision numbers at 20
pixels whereas in the success rate plots, they are ranked by the area
under curve (AUC) scores. The tracking algorithms under the comparison
include ones at high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones at relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers originally use deep
convolutional features, however, to perform fair comparison, we use
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
    at 20 pixels precision. In particular, three algorithms, SAMF,
    DSST, and Struck did about $5\%$ better than ours in accuracy, but
    10-20 times slower. The more recent trackers, ECO and CCOT, on the
    other hand, outperforms {\it E}nKCF by $15\%$ while running at
    10-15 times slower. For the scale adaptation, {\it E}nKCF did
    fourth best in terms of AUC for the success rate plot. It
    outperformed other high-speed trackers by about $20\%$-$25\%$ in
    AUC. In addition, it performed even better than some of the
    lower-speed trackers.  For example, for AUC, {\it E}nKCF
    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
    more than $10$ and $30$ times faster. For the DSST, we believe our
    algorithm outperformed it because, first of all, the DSST uses a
    1-D scale filter and searches the target's scale over 33
    candidates in a scale pool whereas our algorithm uses a 2-D scale
    filter with 3 candidate scales. Learning a 2-D filter resulted in
    learning more spatial information. Second of all, the DSST uses
    only fHoG whereas our algorithm uses both fHoG and color-naming
    features. Learning complementary features such as color and shape
    provided a better understanding of the ROI.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to performance comparison with other trackers, we
also conducted an experiment to see what combination and deployment
order of the KCF works best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. To achieve fair comparison, we
did not use the particle filter. The combination presented at the
$2^{nd}$ column switched the order of deploying $R_{t}^{L}$ and
$R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The combinations with the ``*'' marker ran the
filters on every frame in the listed order. The trackers at the
$7^{th}$ and $8^{th}$ columns ran a translation and a scale filter on
every frame which is similar to the LCT tracker
\cite{ma2015long}.\footnote{To be precise, the LCT tracker comes with
  a re-detection module for a long-term tracking.} This experiment
empirically verified that the way \textit{E}nKCF uses multiple KCFs is
optimal, in terms of both tracking accuracy and run-time
performance. For example, one could achieve $4.26\%$ higher in
accuracy by running $R_{t}^{L}$ and $R_{t}^{S}$, and $R_{s}$ at every
frame (produced 58.16\% for precision at 20 pixels), but this
combination decreases run-time performance to 317 fps (=416fps - 99fps).
\begin{comment}
  \textit{YoungWoo : Should it not be 99fps. Burak: 317=416-99, isn't it?}
\end{comment}
